Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-15 Cover_letter_JPM.tex
table 2 3 4 done
Updates from Overleaf

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

@@

% *** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

@@

>>>>

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
(  )  Answer 2-1
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
Moreover, 
Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
# NDFIP1 (within our 20 candidatte biomarkers), median cut will let NDFIP1 to be kik-out prematurely
# show it's pvalue plot
supplementary Figure \ref{fig:pvaluePlot_NDFIP1} as Rplot_pvaluePlot_NDFIP1.pdf

% supplementary figure
\begin{figure}
    \centering
    \includegraphics{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Caption}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

@@

@@

*** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---
